Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-05-13 paper/paper.tex
introduce ablation study section

\section*{Ablation study}
\subsection*{Is the dataset large enough for evaluation?}

>>>>

\section*{Ablation study}
The previous section described our dataset of audio samples with diverse instruments, mutes, and playing techniques ($N^{\prime}=9346$ isolated notes), as well as the method we adopt to evaluate a given system for timbre similarity retrieval.
Over a cohort of $K=31$ subjects, we reported a precision at rank five (P@5) of $99.0\% \pm 1$.
We now turn to alter certain key choices in the design of the above-described computational blocks, and discuss their respective impacts on downstream performance.

\subsection*{Is the dataset large enough for evaluation?}
